Extracting Information from AGN Variability

### 2017-03-31 Manuscript.tex
Reword last sentence in abstract.
The last sentence in the abstract has been re-worded to flow more
naturally.

% Abstract of the paper
\begin{abstract}
AGN exhibit rapid, high amplitude stochastic flux variability across the entire electromagnetic spectrum on timescales ranging from hours to years. The cause of this variability is poorly understood. We present a method for using variability to (1) measure the time-scales on which flux perturbations evolve and (2) characterize the driving flux perturbations. We model the observed light curve of an AGN as a linear differential equation driven by stochastic impulses. Physically, the impulses could potentially be attributable to local `hot-spots' in the accretion disk---in which case, the linear differential equation describes how the hot spots evolve and dissipate. In this picture, the Green's function of the linear differential equation is the impulse-response function of the accretion disk material to small perturbations of the luminous flux. If accretion disk hot-spots are the root cause of AGN variability, the powerspectrum of the driving stochastic impulses characterizes the timescales on which the hot-spots evolve. We analyze the light curve of the \Kepler AGN Zw 229-15 and find that the observed variability behavior can be modeled as a damped harmonic oscillator perturbed by a colored noise process. The model powerspectrum turns over on time-scale $385$~d. On shorter time-scales, the log-powerspectrum slope varies between $2$ and $4$, explaining the behavior noted by previous studies. We recover and identify both the $5.6$~d and $67$~d timescales reported by previous work. In the local hot-spot picture, these timescales represent the time-scale on which flux perturbations grow, and the time-scale on which flux perturbations decay back to the steady-state flux level respectively. We make the software package used to study light curves using our method, \textsc{k\={a}l\={i}}, available to the community.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
AGN exhibit rapid, high amplitude stochastic flux variability across the entire electromagnetic spectrum on timescales ranging from hours to years. The cause of this variability is poorly understood. We present a Green's Function-based method for using variability to (1) measure the time-scales on which flux perturbations evolve and (2) characterize the driving flux perturbations. We model the observed light curve of an AGN as a linear differential equation driven by stochastic impulses. Physically, the impulses could potentially be attributable to local `hot-spots' in the accretion disk---in which case, the linear differential equation describes how the hot spots evolve and dissipate. In this picture, the Green's function of the linear differential equation is the impulse-response function of the accretion disk material to small perturbations of the luminous flux. If accretion disk hot-spots are the root cause of AGN variability, the powerspectrum of the driving stochastic impulses characterizes the timescales on which the hot-spots evolve. We analyze the light curve of the \Kepler AGN Zw 229-15 and find that the observed variability behavior can be modeled as a damped harmonic oscillator perturbed by a colored noise process. The model powerspectrum turns over on time-scale $385$~d. On shorter time-scales, the log-powerspectrum slope varies between $2$ and $4$, explaining the behavior noted by previous studies. We recover and identify both the $5.6$~d and $67$~d timescales reported by previous work. In the local hot-spot picture, these timescales represent the time-scale on which flux perturbations grow, and the time-scale on which flux perturbations decay back to the steady-state flux level respectively. We make the software package \href{https://github.com/AstroVPK/kali}{\textsc{k\={a}l\={i}}} used to study light curves using our method available to the community.
\end{abstract}
